Graph Exploration and Search

### 2017-11-14 paper.tex
minor

\title*{Graph Exploration and Search}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Davide Mottin\\ Yinghui Wu}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
%
\institute{Davide Mottin， Hasso Plattner Institute, \email{davide.mottin@hpi.de}\\ 
Yinghui Wu, Washington State University, \email{yinghui@eecs.wsu.edu}}
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

\subsection{Graph Search with Keywords (Yinghui)}

>>>>

\title*{Graph Exploration and Search}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Davide Mottin \\ Yinghui Wu}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
%
\institute{Davide Mottin\at Hasso Plattner Institute, \email{davide.mottin@hpi.de}\and  
Yinghui Wu\at Washington State University, \email{yinghui@eecs.wsu.edu}}
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

\subsection{Graph Search with Keywords}
